Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-16 SupportingInformation.Rmd
bug fixed

```{r tab_BMR_asym, echo=F, results="markup"}
tab_BMR_asym<-make_table_stat_fn(data=stat_BMR_ga)
tab_BMR_asym_numbin5<-make_table_stat_fn(data=stat_BMR_ga_numbin5)
knitr::kable(tab_BMR_asym,
             format="pandoc",
             caption = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis (best fit is here Frank with symmetric tail dep)?, numbin=10 \\label{tab_BMR_asym}",
             booktabs=T)

>>>>

```{r tab_BMR_asym, echo=F, results="markup"}
tab_BMR_asym<-make_table_stat_fn(data=stat_BMR_ga)
tab_BMR_asym_numbin5<-make_table_stat_fn(data=stat_BMR_ga_numbin5)

knitr::kable(tab_BMR_asym,
             format="pandoc",
             caption = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis (best fit is here Frank with symmetric tail dep)?, numbin=10 \\label{tab_BMR_asym}",
             booktabs=T)
